Temporal stability in human interaction networks

### 2015-11-02 paper.tex
removidos titulos da secao extra de dicsussoes
arrumado nome, coisa pouca
arrumando resumo

\begin{abstract}
This paper reports on stable properties of human interaction networks,
with benchmarks derived from public email lists.
Activity along time and topology evolution were observed by snapshots in a timeline 
and at different scales.
Our analysis show that the activity across timescales, ranging from seconds to months, is practically the same for all networks.
The most important metrics to the dispersion of participants in the topological measures space are shown to be
are centrality measurements (degree, strength and betweenness),
followed by symmetry-related metrics and then clustering coefficient.
The observed activity of participants follows the expected scale-free trace,
thus yielding the hub, intermediary and periphery classes of vertices by comparison against the Erd\"os-R\'enyi model.
The relative sizes of these three sectors are shown to be essentially the same for all email lists and the same along time.
Typically, 3-12\% of the vertices are hubs, 15-45\% are intermediary and 44-81\% are peripheral vertices.
Similar results for the distribution of participants in the three sectors
and for the relative importance of the topological metrics were obtained for 12 additional networks
from Facebook, Twitter and Participabr.
These properties are consistent with expectations derived from the literature
and may be general for human interaction networks,
which has important implications for establishing a typology of participants based on quantitative criteria.
\end{abstract}

@@

\section{Discussion}
% given the results, and before reaching the conclusions
% what to say?
% --> what is the overall knowledge derived from the results
% --> what are the limitations of this knowledge and of individual results
% --> how should this results carry on is on the next sections.
\subsection{Consecutive scientific research}
% --> research
% textual diferences
% audiovisualization of data
% typologies, sociological critical theory, social psychology

\subsection{Technological applications}
% --> technological 
% resources categorization and recommendation
% document creation
% ontologies for the semantic web

\subsection{Experimental and theoretical aspects of the research}
% --> methods
% Exploratory?
% Hypothesis testing?
% --> contributions
% verifiable
% knowledge
% contextualization in the academic knowledge

% applications 
% experimental and theoretical aspects of the research

>>>>

\begin{abstract}
This paper reports on stable properties of human interaction networks,
with benchmarks derived from public email lists.
Activity along time and topology evolution were observed by snapshots in a timeline 
and at different scales.
Our analysis show that the activity across timescales, ranging from seconds to months, is practically the same for all networks.
The most important metrics to the dispersion of participants in the topological measures space are shown to be
centrality metrics (degree, strength and betweenness),
followed by symmetry-related metrics and then clustering coefficient.
The observed activity of participants follows the expected scale-free trace,
thus yielding the hub, intermediary and periphery classes of vertices by comparison against the Erd\"os-R\'enyi model.
The relative sizes of these three sectors are shown to be essentially the same for all email lists and the same along time.
Typically, 3-12\% of the vertices are hubs, 15-45\% are intermediary and 44-81\% are peripheral vertices.
Similar results for the distribution of participants in the three sectors
and for the relative importance of the topological metrics were obtained for 12 additional networks
from Facebook, Twitter and Participabr.
These properties are consistent with expectations derived from the literature
and may be general for human interaction networks,
which has important implications for establishing a typology of participants based on quantitative criteria.
\end{abstract}

@@

%\section{Discussion}
% given the results, and before reaching the conclusions
% what to say?
% --> what is the overall knowledge derived from the results
% --> what are the limitations of this knowledge and of individual results
% --> how should this results carry on is on the next sections.
%\subsection{Consecutive scientific research}
% --> research
% textual diferences
% audiovisualization of data
% typologies, sociological critical theory, social psychology

%\subsection{Technological applications}
% --> technological 
% resources categorization and recommendation
% document creation
% ontologies for the semantic web

%\subsection{Experimental and theoretical aspects of the research}
% --> methods
% Exploratory?
% Hypothesis testing?
% --> contributions
% verifiable
% knowledge
% contextualization in the academic knowledge
